Towards Pandemic-Scale Ancestral Recombination Graphs of SARS-CoV-2

### 2023-05-12 paper.tex
Yans updates

\subsection{Distribution of recombination breakpoint intervals}
\label{sec:breakpoint_intervals}
It is rarely possible to be precise about the position on the genome at which
a recombinant sequence switches from inheriting from one parent to another.
Even if we observe the recombinant sequence before signficant
divergence occurs (during onward transmission), if the two parent sequences
are similar there is no way to distinguish them. Here we define the
interval for a particular breakpoint as the interval over which the
sequences for the left and right parent nodes are identical. The right-hand
extreme of the interval is chosen by the LS HMM Viterbi algorithm
(Section~\ref{sec:ls}, and the left bound can then be derived by
sequence comparison of the parents.

>>>>

\subsection{Distribution of recombination breakpoint intervals}
\label{sec:breakpoint_intervals}
